Testing Quasar Unification with Clumpy Wind Models

### 2015-12-07 paper_mnras.tex
Removed comments

%  a simple model in which
% quasars are unified by BH mass, Eddington ratio and viewing angle can successfully
% reproduce UV, optical and X-ray properties of {\em both} 
% BALQSO's and normal emission line quasars.

% Geometrical unification pictures have suggested that 
% the BAL fraction can be interpreted as the covering factor
% of an accretion disc wind (refs), and some also propose
% that this disc wind may also be the source of the broad emission
% lines (BELs) seen in QSOs (refs). 
% Alternatively, there are a number of evolutionary models in which
% QSOs spend approximately $20\%$ of their lifetime as BALQSOs in which the outflow
% has a high covering factor (refs). 
% It is also possible that BALQSOs lie in a distinct region
% in terms of Eddington ratio (refs), but this is somewhat refuted 
% by observations (refs). % to e.g. Allen and Eigenvector I papers Ledd of BALQSOs
% Orientation, evolution, black hole mass and eddington ratio 
% may all have an effect on the BAL fraction (refs),  % to e.g. Allen
% and the importance of each must be understood to build up coherent picture.

% The driving mechanism for accretion disc winds is uncertain. The winds responsible 
% for BALs must at least have some line-driven component,
% as very strong resonance lines exert a strong line force on the 
% gas (refs). Line-driven winds are notoriously unstable 
% \citep{lucysolomon1970,macgregor1979,owockirybicki1984,owockirybicki1985}.
% meaning that one may expect an unstable and inhomogenous 
% velocity and density structure (refs). Magnetically driven
% winds may also produce clumpy winds or `clouds' of material which
% are magnetically confined (refs here to Shlosman, Begelman and the like).
% Describe mechanism.

% Evidence for an inhomogenous density structure in an accretion disc wind 
% and/or the broad emission line region comes from multiple sources. 
% Microlensing observations of absorption troughs suggest that different lines of sight 
% exhibit varying velocity components (refs), and BALQSO troughs 
% are known to exhibit variability (refs).

% trend of L_X with radio jets and Sy 1s
% trend of BALs with radio loudness
% see MCGV95

@@

% {\bf ksl - I a a bit torn over whether we add a few 3 sentences to describe the basic idea.  Some will be reading this for the first time.  Items that one would include are that we calculate the radiative transfer in a cylindrical coordinate system of dimension ?? x ??.  We have ionization and spectral cycles. In each cycle, ?? photon bundles are generated. We stop the ionization cycles after they converge, without any details.  I think this would be useful because we introduce terms like ``cell'' later on.', and without some kind of description they have no context}

@@

In order to calculate the photoionization rate, 
we model the SED in a grid cell using the technique described by H13. In this scheme,
the mean intensity, $J_{\nu}$ in a series of $n$ bands is modeled as either a power law or exponential
in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
% \begin{equation}
% J_{\nu,i}=K_{pl}\nu^{\alpha_{pl}},
% \end{equation}
% for a band $i$, or an exponential 
% \begin{equation}
% J_{\nu,i}=K_{exp} e^{(-h\nu/k T_{exp})}.
% \end{equation}
% Here, $K_{exp}$, $K_{pl}$, $T_{exp}$ and $\alpha_{pl}$ are spectral fit parameters
% deduced from the band-limited radiation field estimators.
The ionization rate out of ion $j$ can then be written as 
\begin{equation}
R_{j,j+1}(J)= 
\displaystyle{
n_j \left(C_{j} n_e + 
\sum_{band~i=0}^{n}~
{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
\right),}
\end{equation}
where $\sigma_j$ is the photoionization cross-section, $n_e$
is the electron density and $C_{j}$
represents the collisional ionization coefficient.
The recombination rate {\em into} ion $j$ is given by 
\begin{equation}
R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
\end{equation}
where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
The subscripts denote radiative and 
collisional (three-body) recombination, respectively. 
$T_e$ is the electron temperature.
%% We neglect recombination to and from excited states in the simple-ion calculation. 
For simple-ions, we use a dilute Boltzmann equation to calculate 
the population of level $k$ in ionic stage $j$,
\begin{equation}
\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
\end{equation}
Here $z_j$ is the partition function of ionic stage $j$,
$T_R$ is the effective radiation temperature,
$E_k$ is the energy difference between level $k$ and the ground state,
and $g_k$ is the statistical weight of level $k$. 
We stress that this approximation is not required for ions
treated as macro-atoms.

@@

We include all free-free, bound-free and bound-bound heating
and cooling processes in the model. For radiative transfer purposes
we treat electron scattering in the Thomson limit, 
but take full account of Compton heating and cooling when
calculating the thermal balance of the plasma (see H13).
Adiabatic cooling is included and represents the only
departure from strict radiative equilibrium, but is insignificant 
in most of the outflow.
% It is dealt with self consistently by the spontaneous destruction
% of $k$-packets with a probability

% \begin{equation}
% P_{\rm{adiabatic~destruction}} = \frac{C_{\rm{adiabatic}}}{C_{\rm{total}}},
% \end{equation}
% where $C_{\rm{adiabatic}}$ and ${C_{\rm{total}}}$ represent the 
% adiabatic and total cooling rates in the cell.

@@

To allow for clumping in our outflow we adopt a simple approximation
used successfully in stellar wind modelling, known as 
{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS). 
The key assumption is that typical clump sizes are much smaller than the 
typical photon mean free path, and thus the clumps are 
both geometrically and optically thin. This approach 
allows one to introduce a `volume filling factor', $f_V$. 
The intra-clump medium is assumed to be a vacuum, so the 
density of the clumps is then multiplied by the ``density enhancement'' 
$D=1/f_V$. Opacities, $\kappa$, and emissivities, $\epsilon$, 
can then be expressed as

% \begin{subequations}
% \begin{align}
%         \kappa &= f_V \kappa_C(D) \\
%         \epsilon &= f_V \epsilon_C(D)
% \end{align}
% \end{subequations}
\begin{equation}
\kappa = f_V \kappa_C(D);~~\epsilon = f_V \epsilon_C(D).
\end{equation}
% \kappa = f_V \kappa_C(D) && \epsilon = f_V \epsilon_C(D).
% \end{equation}
Here the subscript $C$ denotes that the quantity is calculated using the 
enhanced density in the clump. The resultant effect is that {\em linear} processes,
such as electron scattering, are unchanged, as $f_V$ and $D$ will cancel out. 
However, any quantity which scales with the {\em square} of density, 
such as collisional excitation or recombination, will increase by a factor of $D$.

% which is defined as 
% \begin{equation}
% D = \frac{1}{f} && 
% \end{equation}
% We then multiply all densities in the model by $D$, and all emitting volumes
% by $f$. This has the effect of enhancing all emissivities and opacities
% that scale with the square of density (such as collisional excitation and recombination) 
% by a factor $D$. All processes that scale linearly with density 
% (such as electron scattering and bound-free opacity)
% will remain unchanged for a given ionization state.

@@

% {\bf We need to describe what we did before getting to results.  We started with parameters similar to those of H14, we created a small grid.  Limits of the grid are given in table 2.  This should be a paragraph or section before this one.  Not all quasars have to have the same parameters and so we have to explain that we have elected to describe one model in detail.  Was our goal to fix the luminosity and see what was required.

% In next sections, we really need to deal with the difference between this class of models and "the model", and especially "our model".  We may need to at least in words discuss whether we have "fine tuned" or not, by saying something about other models.}

@@

% This set of parameters
% was arrived at by conducting a limited grid search over a 
% 5-dimensional parameter space involving the variables
% $r_{min}$, $\theta_{min}$, $f$, $\alpha$ and $R_V$.
% We evaluated these models based on the following
% criteria:
% \begin{itemize}
% \item Does the model maintain the right ionization state to produce strong BALs ($BI > ??$)?
% \item Does significant line emission emerge at low inclinations, with $EW\sim50\AA$ in \civ?
% \item Do H recombination lines appear in the spectrum, $EW\sim50\AA$ in \la?
% \item Do a certain range of angles produce LoBAL features?
% \item Does the model compare favourably to quasar composite spectra?
% \end{itemize}
% In this section, we present one of the most promising models and discuss
% the various successes and failures.
% This allows us to gain insight into fundamental geometrical 
% and physical constraints and assess the potential for unification. 
% The full grid, including output synthetic spectra and plots can be found at
% \url{jhmatthews.github.io/quasar-wind-grid/}.

@@

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/uvspec_estfix.png}
\caption
{
Synthetic spectra at five viewing angles in our model. The coloured lines
show different quasar and BAL quasar composites, and the dotted line shows a disc
only continuum to show the effect of the outflow on the continuum level.  
}
\label{fig:uvspec}
\end{figure*} %fullpage

@@

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/0946_estfix.png}
\caption
{
Synthetic spectra at $72^\circ$ compared to an HST STIS spectrum
of PG0946+301 (Arav et al. 2000). The spectrum is scaled to the flux at 1300\AA\
for direct comparison. 
}
\label{fig:stis}
\end{figure*} %fullpage

@@

% The final possibility is that BALQSOs are not viewed equatorially. 
% This possibility is supported by measurements of the radio spectral indices
% of radio-loud BALQSOs (REF) and attempts to explain the polarisation dichotomy 
% of type 1 and 2 AGN (REF). This would imply that type 1 quasars and BALQSOs are generally 
% viewed from a fairly narrow range of angles ($\sim0$-$50^\circ$), and could also mean 
% the BALQSO fraction requires {\em both} evolutionary and geometric explanations. 
% There is also clear conflict between this explanation and some
% polarisation results \citep{goodrich1995, cohen1995}(BROTHERTON).
% We suggest that future modelling should include predictions of polarisation signatures
% from a detailed radiative transfer simulation, allowing

% When comparing BALQSO and quasar composites, it is apparent
% that they possess remarkably similar line strengths and widths 
% \citep[e.g.][]{weymann1991,reichard2003}.  
% {\bf I think we mean EW here; otherwise I don't understand what we are talking about.  We could say ``line shapes and equivalent widths''.  I also think this requries more than one sentence of introduction.} This presents a challenge to our model, as well as the geometric 
% unification picture in general, because these quantities should vary with inclination angle.
% Limb darkening and foreshortening causes the disc continuum emission to be 
% strongly anisotropic, yet the line emission in our models is much more isotropic. 
% This has the effect of enhancing the line-to-continuum ratios at high inclinations. 
% To construct a scenario where emission 
% line equivalent widths are comparable at all inclinations requires 
% significant fine-tuning when considering a classical thin disc. {\bf Is the previous sentence a throwaway line, or has some person done this.  If so, please reference; if not please delete.}
%An alternative, simpler solution is that the emergent continuum is roughly isotropic.

% Obviously,  one possible solution to this problem is hypothesize a more isotropic distribution for the emergent condition than predicted by a ``classical'' disc. 
% General relativistic effects -- specifically, light bending
% and relativistic beaming -- can cause 
% the accretion disc SED to become more isotropic \citep[e.g.][]{zhang1997,munozdarias2013}.  Incorporating these effects into {\sc PYTHON} would be a very difficult and time-consuming challenge. Therefore, for the purposes of this discussion we have chosen to investigate whether GR effects could produce enough isotropy to address the EW problem, we have generated 
% \ GR disc spectra, we use the code \agn\ \citep{hubeny2000,davishubeny2006,davis2007}. 
% The output flux at three different wavelengths
% as a function of inclination for an \agn\ model with the same disc and BH parameters
% as our clumpy wind model is shown in figure~\ref{fig:f2000}.  The results indicate that 
% the effects of GR on an AGN disc are much less extreme 
% in the UV portion of the spectrum than the calculations
% by \cite{zhang1997} for the X-rays in X-ray binaries.
% The emission for the disks of AGN is still strongly anisotropic.
% GR alone therefore cannot explain the line ratio trends in quasars by making the disc
% emit more isotropically. This supports the findings of \cite{risaliti2011}, 
% who find that EW distributions in quasars are consistent with anisotropic emission 
% from optically thick, 
% disc-like structures for {\em both} the continuum source and BLR. 
% If this is the case, it has a dramatic affect on the intrinsic
% BAL fraction inferred from flux-limited samples \citep{goodrich1997,krolikvoit1998}.
% We will explore these ideas further in a future study.  
% {\bf Wait!  All this says is that there has to be an alternative explanation.
% It is not support for any specific explanation!. This last few sentences should
% be a separate paragraph.  They should start out: An alernative explanation proposed 
% by risalite is that...}

% Figure 5 also shows the spectrum into the optical,
% showing that the outflow produces signiciant optical emission lines
% as well as having a noticeable effect on the continuum shape. This
% is particularly true around the Balmer jump at $3646\AA$ and is due to
% a prominent wind-formed recombination continuum.

@@

\begin{figure*}
% \centering
% \includegraphics[width=1.0\textwidth]{figures/sed_all_balqsos.png}
% \caption
% {
% Broadband SEDs compared to IR and X-ray SEDs for selected BALQSOs 
% from Grupe \& Nousek (2015).
% }
% \label{fig:xray}
\end{figure*}

%{\bf:  Again this section needs an introduction.  Why is this important?}

One of the main motivations for including a treatment of clumping was
to avoid over-ionization of the wind in the presence of strong X-rays. 
Having verified that strong BALs appear in the synthetic spectra,
it is also important to assess whether the X-ray properties of this
next-generation model agree well with quasar and BALQSO samples for the relevant
inclinations.

Figure~\ref{fig:xray} shows the emergent
monochromatic luminosity ($L_\nu$) at 2~keV and 
%$\alpha_{OX}$ 
plotted against $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
% $\alpha_{OX}$ is a spectral index from near UV to X-rays defined by
% \begin{equation}
% \alpha_{OX}=0.3838\log\left(\frac{L_{\nu}(2~keV)}{L_{\nu}(2500~\mbox{\scriptsize{\AA}})}\right),
% \end{equation}
% which effectively represents a near-UV to X-ray flux ratio and a measure of X-ray 
% weakness. 
The monochromatic luminosities are calculated from the synthetic spectra and thus include
the effects of wind reprocessing and attenuation. In addition to model outputs,
we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
samples from Steffen et al. (2006). The best fit relation from Steffen et al. (2006) 
is also shown. For low inclination, `quasar-like' viewing angles,
we now find excellent agreement with AGN samples. The gradient from $20^\circ$ to
$60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
(resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
is opaque, and thus the X-ray source subtends a smaller solid angle at high inclinations
(resulting in a lower $L_{2keV}$ for higher inclinations).

@@

% We can also examine the emergent X-ray spectra from our model. 
% Our code is not yet optimized for producing X-ray spectra, as we do not yet 
% include all lines and levels of e.g. Fe or macro-atom treatments of 
% higher order ions (cf. Sim et al. 2008, 2010). 
% However, the bound-free opacity sources are complete, and comparisons of the shape
% of the heavily absorbed spectra can be useful.
% Figure 6 shows the broadband SED from the model, compared to a number of BALQSO spectra
% from \cite{grupenousek2015} - note that lower mass and super-Eddington sources
% are excluded.

% discuss the figure showing X-ray properties briefly. 
% Present an X-ray spectrum? compare to observations e.g. Giustini?

% {\bf Figures 5 and 6: $L_{2kev}$ v $L_{2500}$ plot and X-ray spectrum compared to Grupe and Nousek (broadband SED?)}

@@

\begin{enumerate}
\item We have introduced a first-order treatment 
of clumping in our model, and found that it can now maintain
the required ionization state while agreeing well with the X-ray
properties of AGN/QSOs.
\smallskip
\item We have shown that the degree of ionization stratification
in the model is sufficient that LoBAL line profiles
are seen at a subset of viewing angles, and Fe~\textsc{ii}
absorption is seen at particularly high inclinations.
\smallskip
\item We find that clumping also causes a significant 
increase in the strength of the  emission
lines produced by the model. This is true both
of collisionally excited resonance lines (such as \civ, \nv)
and recombination lines (such as \la, \ha\ and the Balmer series).
\smallskip
\item The line EWs in our models increase with inclination.
BAL and non-BAL quasar composites have comparable EWs, so our model
fails to reproduce this behaviour.
This is due to a fundamental constraint discussed further in section~\ref{sec:angular}. If the BLR
emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
it is simply not possible to achieve line ratios at low inclinations that are comparable to
those at high inclinations. This is a robust conclusion which 
is independent of the assumed BLR geometry and size.
% \smallskip
% \item We have examined the effect of GR on our disc SED, using the disc atmosphere
% and GR ray-tracing code \agn. While including GR effects
% does cause the disc SED to become slightly more isotropic,
% the effect is not large enough to produce uniform line to continuum ratios
% with viewing angle. We briefly discuss other solutions.
\end{enumerate}
Our work confirms a number of expected outcomes from a geometric unification 
model, and suggests that a simple biconical geometry such as this can come close to 
explaining much of the  phenomenology of quasars. Nevertheless, our conclusions pose 
a clear challenge to the current disc wind unification picture.

% To resolve these challenges, we suggest the following routes forward.
% \begin{enumerate}
% \smallskip
% \item 
% \smallskip
% \item 
% \smallskip
% \item It is clear that the commonly accepted paradigm of an equatorial
% wind with a covering factor of $\sim20\%$ does provide an adequate 
% unified model, as shown here and by other authors 
% (e.g. Marin \& Goosman 2013; DiPompeo et al. 2012a).
% More collimated winds may solve some problems, but must be reconciled with
% polarisation results that suggest an equatorial geometry.
% Computing the polarisation of emergent energy packets in our 
% MCRT code would allow direct comparison
% between outputs from a known geometry and 
% spectropolarimetry of quasars and AGN.
% \smallskip
% \item In addition to spectropolarimetry, one
% of the best observational tools for probing outflow geometries
% is reverberation mapping. We are starting to 
% incorporate methods for predicting the reverberation
% outputs from our models. By comparing with observational data, this
% may provide stronger constraints on outflow geometries.
% \end{enumerate}

>>>>

@@

@@

In order to calculate the photoionization rate, 
we model the SED in a grid cell using the technique described by H13. In this scheme,
the mean intensity, $J_{\nu}$ in a series of $n$ bands is modeled as either a power law or exponential
in frequency $\nu$, with the fit parameters deduced from band-limited radiation field estimators.
The ionization rate out of ion $j$ can then be written as 
\begin{equation}
R_{j,j+1}(J)= 
\displaystyle{
n_j \left(C_{j} n_e + 
\sum_{band~i=0}^{n}~
{\int_{\nu_i}^{~\nu_i+1} \frac{4 \pi J_{\nu,i}\sigma_j(\nu)}  {h \nu} d\nu}
\right),}
\end{equation}
where $\sigma_j$ is the photoionization cross-section, $n_e$
is the electron density and $C_{j}$
represents the collisional ionization coefficient.
The recombination rate {\em into} ion $j$ is given by 
\begin{equation}
R_{j+1,j}(T_e) = (\alpha^j_{RR} + \alpha^j_{CR}) n_{j+1} n_e,
\end{equation}
where each $\alpha^j$ here is the recombination rate coefficient into the ground state of ion $j$.
The subscripts denote radiative and 
collisional (three-body) recombination, respectively. 
$T_e$ is the electron temperature.
%% We neglect recombination to and from excited states in the simple-ion calculation. 
For simple-ions, we use a dilute Boltzmann equation to calculate 
the population of level $k$ in ionic stage $j$,
\begin{equation}
\frac{n_{jk}}{n_j} = \frac{W g_k}{z_j(T_R)} \exp(-E_k/kT_R).
\end{equation}
Here $z_j$ is the partition function of ionic stage $j$,
$T_R$ is the effective radiation temperature,
$E_k$ is the energy difference between level $k$ and the ground state,
and $g_k$ is the statistical weight of level $k$. 
We stress that this approximation is not required for ions
treated as macro-atoms.

@@

We include all free-free, bound-free and bound-bound heating
and cooling processes in the model. For radiative transfer purposes
we treat electron scattering in the Thomson limit, 
but take full account of Compton heating and cooling when
calculating the thermal balance of the plasma (see H13).
Adiabatic cooling is included and represents the only
departure from strict radiative equilibrium, but is insignificant 
in most of the outflow.

@@

To allow for clumping in our outflow we adopt a simple approximation
used successfully in stellar wind modelling, known as 
{\em microclumping} \citep{hamann1998,hamann2008}(MORE REFS). 
The key assumption is that typical clump sizes are much smaller than the 
typical photon mean free path, and thus the clumps are 
both geometrically and optically thin. This approach 
allows one to introduce a `volume filling factor', $f_V$. 
The intra-clump medium is assumed to be a vacuum, so the 
density of the clumps is then multiplied by the ``density enhancement'' 
$D=1/f_V$. Opacities, $\kappa$, and emissivities, $\epsilon$, 
can then be expressed as 
\begin{equation}
\kappa = f_V \kappa_C(D);~~\epsilon = f_V \epsilon_C(D).
\end{equation}
Here the subscript $C$ denotes that the quantity is calculated using the 
enhanced density in the clump. The resultant effect is that {\em linear} processes,
such as electron scattering, are unchanged, as $f_V$ and $D$ will cancel out. 
However, any quantity which scales with the {\em square} of density, 
such as collisional excitation or recombination, will increase by a factor of $D$.

@@

@@

@@

\begin{figure*} %fullpage
\centering
\includegraphics[width=1.0\textwidth]{figures/uvspec_estfix.png}
\caption
{
Synthetic spectra at five viewing angles in our model. The coloured lines
show different quasar and BAL quasar composites, and the dotted line shows a disc
only continuum to show the effect of the outflow on the continuum level.  
HST STIS spectrum of PG0946+301 (Arav et al. 2000)
}
\label{fig:uvspec}
\end{figure*} %fullpage

@@

@@

@@

The main motivation for including a treatment of clumping was
to avoid over-ionization of the wind in the presence of strong X-rays. 
Having verified that strong BALs appear in the synthetic spectra,
it is also important to assess whether the X-ray properties of this
next-generation model agree well with quasar and BALQSO samples for the relevant
inclinations.

Figure~\ref{fig:xray} shows the emergent
monochromatic luminosity ($L_\nu$) at 2~keV and 
plotted against $L_\nu$ at $2500$\AA\ for a number of different viewing angles in our model.
The monochromatic luminosities are calculated from the synthetic spectra and thus include
the effects of wind reprocessing and attenuation. In addition to model outputs,
we also show the BALQSO sample of Saez et al. (2012) and luminous AGN and quasar
samples from Steffen et al. (2006). The best fit relation from Steffen et al. (2006) 
is also shown. For low inclination, `quasar-like' viewing angles,
we now find excellent agreement with AGN samples. The gradient from $20^\circ$ to
$60^\circ$ in our models is caused by a combination of disc foreshortening/limb-darkening 
(resulting in a lower $L_{2500}$ for higher inclinations) and the fact that the disk 
is opaque, and thus the X-ray source subtends a smaller solid angle at high inclinations
(resulting in a lower $L_{2keV}$ for higher inclinations).

@@

@@

\begin{enumerate}
\item We have introduced a first-order treatment 
of clumping in our model, and found that it can now maintain
the required ionization state while agreeing well with the X-ray
properties of AGN/QSOs.
\smallskip
\item We have shown that the degree of ionization stratification
in the model is sufficient that LoBAL line profiles
are seen at a subset of viewing angles, and Fe~\textsc{ii}
absorption is seen at particularly high inclinations.
\smallskip
\item We find that clumping also causes a significant 
increase in the strength of the  emission
lines produced by the model. This is true both
of collisionally excited resonance lines (such as \civ, \nv)
and recombination lines (such as \la, \ha\ and the Balmer series).
\smallskip
\item The line EWs in our models increase with inclination.
BAL and non-BAL quasar composites have comparable EWs, so our model
fails to reproduce this behaviour.
This is due to a fundamental constraint discussed further in section~\ref{sec:angular}. If the BLR
emits fairly isotropically then for a foreshortened, limb-darkened classical thin accretion disc
it is simply not possible to achieve line ratios at low inclinations that are comparable to
those at high inclinations. This is a robust conclusion which 
is independent of the assumed BLR geometry and size.
\end{enumerate}
Our work confirms a number of expected outcomes from a geometric unification 
model, and suggests that a simple biconical geometry such as this can come close to 
explaining much of the  phenomenology of quasars. Nevertheless, our conclusions pose 
a clear challenge to the current disc wind unification picture.
